Python as a machine learning language: experiences from the scikit-learn project

### 2013-04-29 paper.tex
duck typing

>>>>

While object-oriented techniques and design patterns
are used throughout scikit-learn,
they mostly serve to facilitate code reuse and are not considered a project goal.
Where possible, the Python principle of ``duck typing'' is exploited
to simplify the implementation and skip the introduction of superfluous classes.
This allows for extensibility and flexibility at the same time:
user-defined estimators that follow scikit-learn conventions
should be usable in pipelines and other composite objects
without them actually inheriting from scikit-learn base classes.
